---
title: "tidymodels Step 1: Build a model"
author: "Connor French"
date: "5/8/2020"
output: github_document
---

Load packages
```{r warning=FALSE, message=FALSE}
library(tidymodels)
library(readr)
```


Read in urchins data
```{r}
urchins <-
  # Data were assembled for a tutorial 
  # at https://www.flutterbys.com.au/stats/tut/tut7.5a.html
  read_csv("https://tidymodels.org/start/models/urchins.csv") %>% 
  # Change the names to be a little more verbose
  setNames(c("food_regime", "initial_volume", "width")) %>% 
  # Factors are very helpful for modeling, so we convert one column
  mutate(food_regime = factor(food_regime, levels = c("Initial", "Low", "High")))
```


Variables are:
* experimental feeding regime group `food_regime` (`Initial`, `Low`, `High`)
* size in millimeters at the start of the experiment (`initial_volume`), and
* suture width at the end of the experiment (`width`)

Plotting the data
```{r}
ggplot(urchins,
       aes(x = initial_volume, 
           y = width, 
           group = food_regime, 
           col = food_regime)) + 
  geom_point() + 
  geom_smooth(method = lm, se = FALSE) +
  scale_color_viridis_d(option = "plasma", end = .7)
```


## Build and fit a model
Going to use a two-way ANOVA.

Formula:  
`width ~ initial_volume * food_regime`


Set the linear model engine
```{r}
lm_mod <- 
  linear_reg() %>% 
  set_engine("lm")
```

Fit the model
```{r}
lm_fit <- 
  lm_mod %>% 
  fit(width ~ initial_volume * food_regime, data = urchins)

lm_fit
```




Use the **brooms** package's nice `tidy` function to format output as a tibble.
```{r}
tidy(lm_fit)
```

Predict to urchins with an initial volume of 20 ml.
```{r}
new_points <- expand.grid(initial_volume = 20, 
                          food_regime = c("Initial", "Low", "High"))
new_points
```

```{r}
mean_pred <- predict(lm_fit, new_data = new_points)
mean_pred
```



Confidence interval predictions with plot.
```{r}
conf_int_pred <- predict(lm_fit, 
                         new_data = new_points, 
                         type = "conf_int")
conf_int_pred

# Now combine: 
plot_data <- 
  new_points %>% 
  bind_cols(mean_pred) %>% 
  bind_cols(conf_int_pred)

# and plot:
ggplot(plot_data, aes(x = food_regime)) + 
  geom_point(aes(y = .pred)) + 
  geom_errorbar(aes(ymin = .pred_lower, 
                    ymax = .pred_upper),
                width = .2) + 
  labs(y = "urchin size")
```



## Model with a different engine

Contructing a Bayesian linear model.

```{r}
# set the prior distribution
prior_dist <- rstanarm::student_t(df = 1)

set.seed(123)

# make the parsnip model
bayes_mod <-   
  linear_reg() %>% 
  set_engine("stan", 
             prior_intercept = prior_dist, 
             prior = prior_dist) 

# train the model
bayes_fit <- 
  bayes_mod %>% 
  fit(width ~ initial_volume * food_regime, data = urchins)

print(bayes_fit, digits = 5)
```

Look at the parameters table
```{r}
tidy(bayes_fit, intervals = TRUE)
```


Plot predictions
```{r}
bayes_plot_data <- 
  new_points %>% 
  bind_cols(predict(bayes_fit, new_data = new_points)) %>% 
  bind_cols(predict(bayes_fit, new_data = new_points, type = "conf_int"))

ggplot(bayes_plot_data, aes(x = food_regime)) + 
  geom_point(aes(y = .pred)) + 
  geom_errorbar(aes(ymin = .pred_lower, ymax = .pred_upper), width = .2) + 
  labs(y = "urchin size") + 
  ggtitle("Bayesian model with t(1) prior distribution")
```



```{r}

```

